A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-22 doc/paper/paper.tex
LaTeX consistency, and NEF sentence rewrite

\subsection{The Neural Engineering Framework}
The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method of mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
We now summarize the relevant aspects of this framework, ordered by its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.

@@

\subsubsection{Principle 2: Transformation}
By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} 
= \abs{f(x) - \hat x}$ arbitrary linear and nonlinear functions $f(x)$ can be approximated in the connections between neural populations.

>>>>

\subsection{The Neural Engineering Framework}
The Neural Engineering Framework~\cite<NEF;>{eliasmith2003} is a method of mapping a cognitive model, described using mathematical equations, onto a spiking neural network.
We now describe the aspects of this framework that are relevant to this work, by summarizing its three principles: \emph{representation}, \emph{transformation}, and \emph{dynamics}.

@@

\subsubsection{Principle 2: Transformation}
By finding alternate decoding weights $d^f_i$ with the error given by $E_{f(x)} = \abs{f(x) - \hat x}$, arbitrary linear and nonlinear functions $f(x)$ can be approximated in the connections between neural populations.
